---
title: "linear model from Web"
author: "Matt Diaz"
date: " Spring 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```
# Introduction:

We will produce three equation models to get   
1. sim score based on arm strength.   
2. sim score based on grip,    
3. sim score based on both arm and grip strength.    

For each model we will predict sim for arm = 88, grip = 94 

# Methods: 
We have numerical respinses (sim score) and numerical explanatory variables (arm and grip strength)
so we use thre numercial~numerical helper file

## Model 1 SIM~ARMS

## Results
### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

There is a positive relationship between SIMS and ARM. If this were a perfect linear relationship then all of these plots would be in a straight line. The correlation may be around 0.8.  

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

This is the degree of correlation between arm strength and sims score. A strong correlation is 1 and a weak correlation would be 0. 

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The p-value for the coefficient of arm is smaller than .05. This means that the coefficient is highly significant.  

#### Predict at target point

```{r}
SIMSpredict= predict.lm(model.1, newdata= data.frame(ARM=88,GRIP=94), interval = "confidence") 
print(SIMSpredict)
```

The prediction for ARM= 88, GRIP= 94 is 0.71. 

#### scatterplot with model fit
  
```{r}
plot(SIMS~ARM,data=data)
abline(model.1, col="red")
```

This is a scatter plot with a function on it. At ARM strength 88 the 95 percent confidence interval is between .48 and .92. 

## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
m = data.frame(data['GRIP'],data['ARM'],data['SIMS'])
cor(m)
```

The table shows that SIMS correlates with GRIP in a positive manner, (0.64) and SIMS correlates with ARM also in a positive manner, (0.69). This says these variables are usefeul in predicting SIMS. 

```{r}
plot(data$GRIP, data$ARM)
```

plot shows GRI and ARM are nor independent, so this is not necessarily a good model.   
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 = lm(SIMS~GRIP+ARM, data = data)
print(summary(model.3))

```



#### predict model.3 at target point
  
```{r}
newPoint = data.frame(GRIP = 94, ARM = 88)
predict.lm(model.3, newPoint, interval = 'prediction' )
```
  
The 95% confidence interval is SIMS is between -2.13 and 2.43 since this interval contains zero, we do not have a very good prediction for SIMS.   

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

